VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-29 snapshot_system/paper_analysis.tex
shortened

\begin{table}[htbp]
\centering
\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belonging to  PDS\\
\hline
$p$ & the number of machines in the cluster\\
\hline
$V$ & the average number of VMs per machine\\
\hline
$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
\hline
$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$ & the average number  of non-PDS FSBs blocks in a VM for VC\\
\hline
$N_2$ & the average number  of PDS FSBs in a VM for VC\\
\hline
$N_o$ & the average number  of FSBs  in a VM for VO\\
\hline
A(r) & the availability of an FSB  with replication degree $r$\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

@@

We analyze the impact of the above VM centric design on fault isolation and compare it
with a VM oblivious design.
Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
$r=3$ is a typical setting in distributed file systems~\cite{googlefs03,hdfs10}.
Let $r_c$ be the replication degree of file blocks for PDS. 
Additional parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
%The replication degree of the backup storage 
%is $r$ for regular file system blocks and 
%Since $\sigma$ is small (e.g.  2\% in our experiments),  
%the impact of replication on storage increase is very small even 
%when choosing  $r_c/r$ ratio as 2 or 3.

@@

Now we  assess  the impact of losing $d$ machines 
to the VM centric and oblivious approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
%We use an FSB rather than a deduplication
%data chunk as our unit of failure because the DFS keeps
%file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we estimate
the number of file system blocks per VM and the probability of losing a snapshot file system 
block of a VM in each approach as follows.
%As illustrated in Figure~\ref{fig:share},
%we build a bipartite graph representing the association from unique file system blocks
%to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
%if this block is used by the VM.

@@

\comments{
%Moved up in the strategy subsection
We could consider a third approach (call it VO+), adopting the VO approach, and
then relying on filesystem features to provide extra replication to popular
blocks, without the extra complexity of separating popular and non-popular
data. The problem with this VO+ approach is that without separating the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system. Because the popular blocks
are dispersed, there are very few popular FSBs. The end result is that we
either have to add extra replication on unpopular chunks to ensure the popular
chunks have sufficient replication, or we have to accept a reduced replication
factor on popular chunks. This explains why we must separate the PDS and
non-PDS data in our system to achieve the desired $r_c/r$ ratio (though both
can be stored on the same DFS).
}
For VC, each VM has an average number $N_1$ of non-PDS FSBs
and  has  an average of  $N_2$ PDS FSBs. 
Each non-PDS FSB is associated with one VM
 and  we denote that PDS FSBs are
shared by an average of $V_c$ VMs. 
%Let $s$ be the average number of chunks per file system block, 
%$V$ be the average number of VMs hosted on each machine. 
Then, 
\[
V pN_1 s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
V pN_2 s  \approx c_u \sigma V_c.
\]

For VO, each VM has an average of $N_o$ FSBs
and let $V_o$ be the average number of VMs shared by each FSB.
\[
V pN_o s  = (c- E_o(c-c_u) ) V_o.
\]

Since each FSB (with default size $64MB$) contains many chunks (on average 4KB),
each FSB contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
\[
\frac{N_1}{N_o} \approx  \frac{1-E_o}{(1-E_c) V_o}.
\] 
When $E_c$ is close to $E_o$,
%as demonstrated in Section~\ref{sect:evaldedup},
$N_1$ is much smaller than $N_o$. 
%When there is a failure in FSBs with replication degree $r$
%and there is no failure for PDS data with more replicas,   a VM in
%the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO
and  $N_1$ is indeed  much smaller than $N_o$ in our tested dataset.  
%In fact, $N_1 +N_2 < N_o$. 
%This is likely because the PDS FSBs tightly pack data used by many VMs, 
%which decreases the overall number of FSBs required to backup a VM.
%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
%VMs sharing each file block on average in VO.

@@

\comments{
\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of VMs sharing a 64MB FSB in VO and in VC.}
  \label{fig:fsb-links}
\end{figure}

}

>>>>

\begin{table}[htbp]
\centering
\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
%\hline
%$k$ &  the number of top most popular chunks selected for deduplication\\ 
%\hline
%$c$ &  the total amount of data chunks in a cluster of VMs\\ 
%\hline
%$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
%\hline
%$f_i$ &  the frequency for the $i$th most popular fingerprint\\
%\hline
%$\delta$ &  the percentage of duplicates detected in local deduplication\\
%\hline
%$\sigma$ & = percentage of unique data  belonging to  PDS\\
\hline
$r$, $r_c$ & replication degree of non-PDS, and PDS file blocks\\
\hline
$n$, $p$ & no. of virtual and physical machines in the cluster\\
%\hline
%$V$ & the average number of VMs per machine\\
%\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$, $N_2$ & the average number  of non-PDS and PDS file blocks in a VM for VC\\
\hline
$N_o$ & the average number  of file blocks  in a VM for VO\\
\hline
A(r) & the availability of a file block with replication degree $r$\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

@@

We analyze the impact of the above VM centric design on fault isolation and compare it
with a VM oblivious design.
%Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
%$r=3$ is a typical setting in distributed file systems~\cite{googlefs03,hdfs10}.
%Let $r_c$ be the replication degree of file blocks for PDS. 
Parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
%The replication degree of the backup storage 
%is $r$ for regular file system blocks and 
%Since $\sigma$ is small (e.g.  2\% in our experiments),  
%the impact of replication on storage increase is very small even 
%when choosing  $r_c/r$ ratio as 2 or 3.

@@

Now we  assess  the impact of losing $d$ machines 
to the VM centric and oblivious approaches.  
%A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
%We use an FSB rather than a deduplication
%data chunk as our unit of failure because the DFS keeps
%file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we estimate
the number of file system blocks per VM and the probability of losing a snapshot file system 
block of a VM in each approach as follows.
%As illustrated in Figure~\ref{fig:share},
%we build a bipartite graph representing the association from unique file system blocks
%to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
%if this block is used by the VM.

@@

For VC, each VM has an average number $N_1$ of non-PDS FSBs
and  has  an average of  $N_2$ PDS FSBs. 
Each non-PDS FSB is associated with one VM
 and  we denote that PDS FSBs are
shared by an average of $V_c$ VMs. 
Then, 
\[
n* N_1   \approx \mbox{ No of non-PDS file system blocks} 
\]

For VO, each VM has an average of $N_o$ file system blocks
and let $V_o$ be the average number of VMs shared by each FSB.
\[
n *N_o   =  V_o *\mbox{ No of file system blocks} 
\]

Since the number of PDS file system blocks is small, 
and the deduplication efficiency of VC is very close to that of VO,
the number of non-PDS file blocks in VC is close to the number of file blocks in VO.
Then
\[
\frac{N_o}{N_1} \approx  V_o.
\]
Thus $N_o >> N_1$.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO
and  $N_1$ is indeed  much smaller than $N_o$ in our tested dataset.

%In fact, $N_1 +N_2 < N_o$. 
%This is likely because the PDS FSBs tightly pack data used by many VMs, 
%which decreases the overall number of FSBs required to backup a VM.
%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
%VMs sharing each file block on average in VO.

@@
